Transfer Learning in Visual and Relational Reasoning\\ (Supplementary Material)

### 2019-11-22 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
Fixed appendix in both supplementary and arxiv. Added results from SoftPaths to the arxiv version. Added a comment in the main body as well.

%%%%%%%%% TITLE
\title{Transfer Learning in Visual and Relational Reasoning\footnote{%
		Major portion of this work was done when all the authors were at IBM Research AI (Almaden)}}

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
\author{%
	T.S. Jayram\thanks{IBM Research AI.
		Location: \textit{Almaden Research Center, San Jose, CA, USA}.} \and  
	Vincent Marois\thanks{IBM Research AI. 
		Location: \textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \and 
	Tomasz Kornuta\thanks{Nvidia Research. 
		Location: \textit{Santa Clara, CA, USA}.} \and 
	Vincent Albouy\thanks{} \and 
	Emre Sevgen\thanks{University of Chicago.}  \and 
	Ahmet Ozcan\footnotemark[2]
}

@@

\bibliographystyle{alpha}
\bibliography{bibliography}

\newpage
\input{appendix}

>>>>

%%%%%%%%% TITLE
\title{Transfer Learning in Visual and Relational Reasoning\footnote{%
		This work was primarily done at IBM Research AI.}}

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
\author{%
	T.S. Jayram\thanks{IBM Research AI. \textit{Almaden Research Center, San Jose, CA, USA}.} \and  
	Vincent Marois\thanks{IBM Research AI. \textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \and 
	Tomasz Kornuta\thanks{Nvidia Research. \textit{Santa Clara, CA, USA}.} \and 
	Vincent Albouy\thanks{} \and 
	Emre Sevgen\thanks{Citrine Informatics}  \and 
	Ahmet Ozcan\footnotemark[2]
}

@@

\bibliographystyle{alpha}
\bibliography{../bibliography}

\newpage
\appendix

\input{appendix}

### 2019-11-22 Transfer_Learning/arxiv_version/experiments.tex
Fixed appendix in both supplementary and arxiv. Added results from SoftPaths to the arxiv version. Added a comment in the main body as well.

%More details on the composition of these datasets is available in Appendix \ref{sec:datasets-desc}.

@@

We trained SAMNet using 8 reasoning steps and external memory of 8 address locations, each storing an array of 128 floats. 
%We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in the supplementary material.%Appendix~\ref{sec:cog-all-results}.

@@

@@

Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in the supplementary material.%Appendix \ref{sec:full-cogent-results}.

@@

An additional set of experiments, for which results are available in the supplementary material,
%Appendix \ref{sec:full-cogent-results}
fine-tune the model trained on all tasks on each task $t$ respectively.
%Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the fine-tuned task and the drop, if any, on other tasks.
Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks. Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.

>>>>

More details on the composition of these datasets is available in Appendix~\ref{sec:datasets-desc}.

@@

We trained SAMNet using 8 reasoning steps and external memory of 8 address locations, each storing an array of 128 floats. 
%We have also carried out experiments with different numbers of reasoning steps and memory size, but this goes beyond the scope of this paper.
We compared our results with the baseline model introduced in the same paper as the COG dataset~\cite{yang2018dataset}.
The most important results are highlighted in~\cref{fig:samnet_cog_detailed}; full comparison can be found in 
Appendix~\ref{sec:cog-all-results}.

@@

Appendix~\ref{sec:cog-all-results} also includes the task-by-task performance of ``SoftPaths'' model~\cite{haurilet2019s} on the Canonical variant of the COG dataset, on which it achieves on overall accuracy of 96.1\%. This model is however not recurrent, therefore, it is unsuitable for temporal transfer learning, in contrast to SAMNet or the baseline model of~\cite{yang2018dataset}.

@@

Noticeable results are shown in~\cref{fig:CoGenT-results}, while the complete set is available in Appendix~\ref{sec:full-cogent-results}.

@@

An additional set of experiments, for which results are available in Appendix~\ref{sec:full-cogent-results},
fine-tune the model trained on all tasks on each task $t$ respectively.
%Given the initial training on all tasks, we were interested in the tradeoff between the performance gain, if any, on the fine-tuned task and the drop, if any, on other tasks.
Fine-tuning did not demonstrate a clear benefit (except for \textit{Count}, where the accuracy increased by 1.5 pt) without hurting performance on the other tasks. Nevertheless, these experiments leave open the possibility that joint training of tasks may potentially benefit from using weighted sampling towards the tail end with more emphasis on samples from less performing task groups, similar to~\cite{guo2018dynamic, kendall2018multi}.

### 2019-11-22 Transfer_Learning/cvpr_submission/appendix.tex
Fixed appendix in both supplementary and arxiv. Added results from SoftPaths to the arxiv version. Added a comment in the main body as well.

\begin{table*}[htb]
\centering
	\begin{adjustbox}{width=\columnwidth}
	\begin{tabular}{lcccccccccc}
		\toprule
		Model & & SAMNet & && && Baseline Model&& \\
		\cmidrule{2-5} \cmidrule{7-11} 
		&&&&& & paper & code & code & paper&\\
		\cmidrule{7-9} \cmidrule{10-11}
		Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
		Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
		Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
		\midrule

		Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1 \\

		\midrule

		AndCompareColor			&	93.5	&	82.7	&	89.2	&	80.6	&	&	81.9	&	57.1	&	60.7	&	51.4	 \\
		AndCompareShape			&	93.2	&	83.7	&	89.7	&	80.1	&	&	80.0	&	53.1	&	50.3	&	50.7 \\
		AndSimpleCompareColor		&	99.2	&	85.3	&	97.6	&	99.4	&	&	99.7	&	53.4	&	77.1	&	78.2 \\
		AndSimpleCompareShape		&	99.2	&	85.8	&	97.6	&	99.2	&	&	100.0	&	56.7	&	79.3	&	77.9 \\
		CompareColor			&	98.1	&	89.3	&	95.9	&	99.7	&	&	99.2	&	56.1	&	67.9	&	50.1 \\
		CompareShape			&	98.0	&	89.7	&	95.9	&	99.2	&	&	99.4	&	66.8	&	65.4	&	50.5	 \\
		Exist				&	100.0	&	99.7	&	99.8	&	99.8	&	&	100.0	&	63.5	&	96.1	&	99.3 \\
		ExistColor			&	100.0	&	99.6	&	99.9	&	99.9	&	&	99.0	&	70.9	&	99	&	89.8 \\
		ExistColorOf			&	99.9	&	95.5	&	99.7	&	99.8	&	&	99.7	&	51.5	&	76.1	&	73.1 \\
		ExistColorSpace			&	94.1	&	88.8	&	91.0	&	90.8	&	&	98.9	&	72.8	&	77.3	&	89.2 \\
		ExistLastColorSameShape		&	99.5	&	99.4	&	99.4	&	98.0	&	&	100.0	&	65.0	&	62.5	&	50.4 \\
		ExistLastObjectSameObject	&	97.3	&	97.5	&	97.7	&	97.5	&	&	98.0	&	77.5	&	61.7	&	60.2 \\
		ExistLastShapeSameColor		&	98.2	&	98.5	&	98.8	&	97.5	&	&	100.0	&	87.8	&	60.4	&	50.3 \\
		ExistShape			&	100.0	&	99.5	&	100.0	&	100.0	&	&	100.0	&	77.1	&	98.2	&	92.5 \\
		ExistShapeOf			&	99.4	&	95.9	&	99.2	&	99.2	&	&	100.0	&	52.7	&	74.7	&	72.70 \\
		ExistShapeSpace			&	93.4	&	87.5	&	91.1	&	90.5	&	&	97.7	&	70	&	89.8	&	89.80 \\
		ExistSpace			&	95.3	&	89.7	&	93.2	&	93.3	&	&	98.9	&	71.1	&	88.1	&	92.8 \\
		GetColor			&	100.0	&	95.8	&	99.9	&	100.0	&	&	100.0	&	71.4	&	83.1	&	97.9 \\
		GetColorSpace			&	98.0	&	90.0	&	95.0	&	95.4	&	&	98.2	&	71.8	&	73.	&	92.3 \\
		GetShape			&	100.0	&	97.3	&	99.9	&	99.9	&	&	100.0	&	83.5	&	89.2	&	97.1	 \\
		GetShapeSpace			&	97.5	&	89.4	&	93.9	&	94.3	&	&	98.1	&	78.7	&	77.3	&	90.3 \\
		SimpleCompareShape		&	99.9	&	91.4	&	99.7	&	99.9	&	&	100.0	&	67.7	&	96.7	&	99.3 \\
		SimpleCompareColor		&	100.0	&	91.6	&	99.80	&	99.9	&	&	100.0	&	64.2	&	90.4	&	99.3 \\
		\bottomrule
		\end{tabular}
		\end{adjustbox}
	\caption{COG test set accuracies for SAMNet and baseline model~\cite{yang2018dataset}. Below `paper' denotes results from~\cite{yang2018dataset} with further author clarifications (private communication) while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}.}
	\label{tab:all-results}
\end{table*}

>>>>

\begin{table*}[htb]
	\centering
	\begin{adjustbox}{width=\textwidth}
		\begin{tabular}{l c c c c c c c c c}
			\toprule
			Model & \multicolumn{4}{c}{SAMNet} &  &\multicolumn{4}{c}{Baseline Model} \\
			\cmidrule(lr){2-5} 
			\cmidrule(lr){7-10} 
			&&&&& & paper & code & code & paper\\
			\cmidrule(lr){7-10} 
			Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
			Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
			Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
			\midrule			
			Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1 \\ 
			\midrule 
			AndCompareColor			&	93.5	&	82.7	&	89.2	&	80.6	&	&	81.9	&	57.1	&	60.7	&	51.4	 \\
			AndCompareShape			&	93.2	&	83.7	&	89.7	&	80.1	&	&	80.0	&	53.1	&	50.3	&	50.7 \\
			AndSimpleCompareColor		&	99.2	&	85.3	&	97.6	&	99.4	&	&	99.7	&	53.4	&	77.1	&	78.2 \\
			AndSimpleCompareShape		&	99.2	&	85.8	&	97.6	&	99.2	&	&	100.0	&	56.7	&	79.3	&	77.9 \\
			CompareColor			&	98.1	&	89.3	&	95.9	&	99.7	&	&	99.2	&	56.1	&	67.9	&	50.1 \\
			CompareShape			&	98.0	&	89.7	&	95.9	&	99.2	&	&	99.4	&	66.8	&	65.4	&	50.5	 \\
			Exist				&	100.0	&	99.7	&	99.8	&	99.8	&	&	100.0	&	63.5	&	96.1	&	99.3 \\
			ExistColor			&	100.0	&	99.6	&	99.9	&	99.9	&	&	99.0	&	70.9	&	99	&	89.8 \\
			ExistColorOf			&	99.9	&	95.5	&	99.7	&	99.8	&	&	99.7	&	51.5	&	76.1	&	73.1 \\
			ExistColorSpace			&	94.1	&	88.8	&	91.0	&	90.8	&	&	98.9	&	72.8	&	77.3	&	89.2 \\
			ExistLastColorSameShape		&	99.5	&	99.4	&	99.4	&	98.0	&	&	100.0	&	65.0	&	62.5	&	50.4 \\
			ExistLastObjectSameObject	&	97.3	&	97.5	&	97.7	&	97.5	&	&	98.0	&	77.5	&	61.7	&	60.2 \\
			ExistLastShapeSameColor		&	98.2	&	98.5	&	98.8	&	97.5	&	&	100.0	&	87.8	&	60.4	&	50.3 \\
			ExistShape			&	100.0	&	99.5	&	100.0	&	100.0	&	&	100.0	&	77.1	&	98.2	&	92.5 \\
			ExistShapeOf			&	99.4	&	95.9	&	99.2	&	99.2	&	&	100.0	&	52.7	&	74.7	&	72.70 \\
			ExistShapeSpace			&	93.4	&	87.5	&	91.1	&	90.5	&	&	97.7	&	70	&	89.8	&	89.80 \\
			ExistSpace			&	95.3	&	89.7	&	93.2	&	93.3	&	&	98.9	&	71.1	&	88.1	&	92.8 \\
			GetColor			&	100.0	&	95.8	&	99.9	&	100.0	&	&	100.0	&	71.4	&	83.1	&	97.9 \\
			GetColorSpace			&	98.0	&	90.0	&	95.0	&	95.4	&	&	98.2	&	71.8	&	73.	&	92.3 \\
			GetShape			&	100.0	&	97.3	&	99.9	&	99.9	&	&	100.0	&	83.5	&	89.2	&	97.1	 \\
			GetShapeSpace			&	97.5	&	89.4	&	93.9	&	94.3	&	&	98.1	&	78.7	&	77.3	&	90.3 \\
			SimpleCompareShape		&	99.9	&	91.4	&	99.7	&	99.9	&	&	100.0	&	67.7	&	96.7	&	99.3 \\
			SimpleCompareColor		&	100.0	&	91.6	&	99.80	&	99.9	&	&	100.0	&	64.2	&	90.4	&	99.3 \\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption{COG test set accuracies for SAMNet and the baseline model~\cite{yang2018dataset}. The `paper' columns for the baseline model denote results taken from~\cite{yang2018dataset} along with some further author clarifications (private communication) to obtain the performance on individual task types while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}.}
	\label{tab:all-results}
\end{table*}
